Our product aims to tackle two grand challenges;  
'Ageing society', to help people improve their diet and live longer lives and  
'Artificial Intelligence and data', to use AI to prevent chronic diseases.  
Chronic degenerative diseases (CDDs) are estimated to cause almost 17 million premature deaths a year worldwide [1] and  
globally over 70\% of public health spending is used to manage CDDs [1].  
Even when not leading to deaths, CDDs drastically reduce an individual's quality of life [2].  
Nutrition is a key contributor to an individual's health and CDDs are attributed in part to poor nutrition [1].  
Unfortunately, getting proper nutrition can sometimes be a problem of access and, 
while enough food is produced to feed everyone, over a billion tons of food is wasted per year [3]. 
Much of this waste occurs before the consumer, but regardless reducing food waste at home remains important. 
Ultimately, improving one's diet while minimizing food waste is time intensive and challenging, 
which is why our product aims to simplify this task.  
 
Our product is the Smart Fridge, which aims to help the user "eat better without thinking about it."  
It is a device which tracks the inventory of a fridge and presents the data live on an app that the user can access remotely.  
This means that they never have to guess what is in their fridge and will be presented with insights about the fridge's contents,  
such as recipe recommendations, nutritional facts, or expiry dates reminders. 
All this information will aid our users in living healthier lives, saving time, and preventing food waste.  

The Smart Fridge stands out from other products on the market as using computer vision to automatically track the inventory 
has not been explored in the consumer space and other food inventory systems require more interaction from the user.  

By January 2023 we will have produced a working proof of concept with documentation. 
