

\input{tables/contrib.tex}


After getting home from a long day of work, the last thing you want to do is go to the shop because you have run out of milk or another product.
The Smart Fridge aims to help the user “eat better without thinking about it” by keeping track of the inventory of the fridge and presenting that data live on a website.
Furthermore, the website will recommend recipes and nutritional information relevant to the contents of their fridge and notify users when items are about to expire.
The product aims to tackle two grand challenges; 'Ageing society', to help people improve their diet and live longer lives and 'Artificial Intelligence and data' to use AI to prevent chronic diseases.
The information stored on the website will aid our users in living healthier lives, saving time, and preventing food waste.  

Chronic degenerative diseases (CDDs) are estimated to cause almost 17 million deaths a year around the world [DI RENZO DIET AND NUTRITION REFERENCE] and 70\% of public health spending is used to manage these CDDs.
While not being able to directly cure these diseases, healthier lifestyle choices such as proper nutrition can greatly help reduce the chances of these diseases occurring.
While CDDs may not all be lethal, they can still rapidly reduce an individual's quality of life [DIGITAL HEALTH 2022 REFERENCE].
Sometimes, it can be difficult to access these nutrients due to food shortages as well as supply issues and with over a billion tons of wasted food a year [FOOD WASTAGE FOOTPRINTS 2013 REFERENCE], it's becoming more and more important for the consumer to care about their own individual footprint.  

By allowing the user to view their fridge contents and browse through recommended recipes, they can achieve the required nutrition to stay healthy while reducing waste.