% Please add the following required packages to your document preamble:
% \usepackage{longtable}
% Note: It may be necessary to compile the document several times to get a multi-page table to line up properly
\begin{longtable}[c]{lll}
    \caption{}
    \label{tab:my-table}\\
    Sub-System Name &
      Sub-System Aims &
      Dependency \\
    \endfirsthead
    %
    \endhead
    %
    HX711 Load Cell Weight Sensor &
      The Weight Sensor measures the weight of all items placed on top of it. The value is sent to the ESP32. &
      Needs between 3.3V and 5V to operate. \\
    HAL Sensor &
      Sends an ON/OFF state to the ESP32 when the fridge door is open. &
      Needs between 2.8V and 6V to operate. \\
    Piezo Buzzer &
      When the doors been open after a limit, the buzzer will sound. &
      The ESP32 sends a square PWN signal to the buzzer. The frequency is set by the ESP32 code. \\
    LED’s &
      Lights the fridge when it opens. &
      Needs between 5V to operate. \\
    ESP32 Microprocessor &
      Controls the operation of the sensors for the fridge. Packets the sensor data in a JSON packet which is sent to the Raspberry PI. Needs to calculate the direction of the item using the change in weight value. &
      Needs 5V power from the step-down circuit built on the PCB. Requires weight value from the weight sensor and the ON/OFF state from the HAL sensor. \\
    Raspberry PI &
      Uses web camera image and OpenCV to detect the items entering the fridge. Sends the inventory data to the cloud database using GraphQL communication. &
      Needs 5V power from the step-down circuit built on the PCB. Requires web camera image of inside the fridge. Requires JSON packet containing item direction, ON/OFF state from the HAL sensor and alarm state. This is sent via UART using Serial communication. \\
    Web Camera &
      Captures images of the product as it enters and exits the fridge. &
      5V power connected via USB from the Raspberry PI. \\
    PostgreSQL &
      Stores the inventory data sent from the Raspberry PI. &
      Receives the inventory data from the Raspberry PI via GraphQL communication.
    \end{longtable}